\chapter{Background}\label{chap:background}

Sample citation: \cite{backens2018zhcalculus}

\section{The ZX-calculus}\label{sec:zx-background}
\ROUGH{In \cite{CD1}\cite{CD2}, the ZX-calculus was introduced, forming the
first of a family of diagrammatic languages for reasoning about quantum logic.
It is still the most accessible and well-explored of these languages, especially
with the availability of \cite{CKbook} , a comprehensive textbook on the subject.
Therefore, before going into the details of any particular language, it helps to
be familiar with the ZX-calculus.}

\TODO{Add reference to Penrose graphical notation, with proper cite}
\begin{TODOLIST}
Introduce here, in order:
\begin{enumerate}
\item Generators (incl. phase states)
\item Customary interpretation of the generators.
\item Only Topology Matters
\item The spider laws (incl. phase spiders)
\item Strong complementarity (mention "homomorphism" and "bialgebra")
\item Weak/Hopf complementarity as result of strong and OTM
\item The axioms (table)
\item The laws (table)
\item Graph states? As application and for backref next section.
\end{enumerate}
\end{TODOLIST}

\section{The ZH-calculus}\label{sec:zh-background}

\begin{TODOLIST}
Introduce here, (in order?):
\begin{enumerate}
\item (cite)
\item Generators with their intended interpretation.
\item OTP, spider laws, bialg\&Hopf as in ZX
\item The axioms (table)
\item Toffoli
\item Hypergraph states? Original motivation, but not prominent here.
\end{enumerate} 
\end{TODOLIST}

\section{The ZX$\Delta$-calculus}\label{sec:zxd-background}

\begin{TODOLIST}
\begin{enumerate}
\item As ZX, but add triangle (cite)
\item Triangle and its interpretation.
\item The axioms (table)
\end{enumerate}
\end{TODOLIST}

\NOTE{Should ZW also be introduced? Not directly necessary, but very welcome
background and might be useful to be able to refer to as motivation for some
steps. Also, forms backbone of ZX$\Delta$ completeness.}

\section{!-box notation}\label{sec:bangbox}

\begin{TODOLIST}
\begin{enumerate}
\item The !-box, motivation, origin (cite), and semantics
\item Restate laws (which?) !-boxed.
\item !-box induction (cite), preferably with example.
\end{enumerate}
\end{TODOLIST}
